### 2015-03-15 translation.tex
some fixes

First, \whoop runs Chauffeur, a Clang-frontend that we developed to perform two tasks: (i) visit the abstract syntax tree (AST) of the original program and extract all available entry point identifier names in the given module, together with the identifier names of their corresponding kernel callbacks; and (ii) instrument the original program with a function that calls all available entry points. This function acts as the main entry point to the module after the latter has been registered with the kernel. This simple rewriting does not alter the semantics of the original program, is required so that Clang does not compile away any uncalled entry points (because we closed the environment using stub functions) and is also later used by \whoop to help instrument asynchronous calls to entry points and create checker procedures (see Sections~\ref{tech:analysis} and~\ref{tech:bugfinding}). The output is a file that contains information regarding the entry points and a file with the rewritten program.

>>>>

First, \whoop runs Chauffeur, a Clang-frontend that we developed to perform two tasks: (i) visit the abstract syntax tree (AST) of the original program and extract all available entry point identifier names in the given module, together with the identifier names of their corresponding kernel callbacks; and (ii) instrument the original program with a function that calls all available entry points. This function acts as the main entry point to the module after the latter has been registered with the kernel. This simple rewriting does not alter the semantics of the original program, is required so that Clang does not compile away any uncalled entry points (because we closed the environment using stub functions) and is also later used by \whoop to help instrument asynchronous calls to entry points and create checker procedures (see Sections~\ref{staticanalysis} and~\ref{bugfinding}). The output is a file that contains information regarding the entry points and a file with the rewritten program.
